Global study of well-being and internet adoption | Online analysis supplement

### 2021-11-22 04-model-inference.Rmd
Load models from file

```{r}
# Read models from files to data frames
```

@@

```{r}
tmp_coefs <- fits_1c %>% 
  mutate(
    out = map(
      fit, 
      ~hypothesis(
        .x, 
        # Rescale coefficient here to years on %
        # Note self harm doesnt work now
        c(str_glue("val_year = 0")),
        scope = "coef",
        group = "region"
      )$hypothesis
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(result = str_glue('**{Estimate}**<br>[{CI.Lower}, {CI.Upper}]')) %>% 
  select(cause, region = Group, result)
tmp_coefs
pseudo_gwp <-
  bind_rows(
    distinct(gbd, region, year, val = NA) %>% 
      crossing(
        cause = fct_inorder(
          c(
            "Negative\nexperiences", 
            "Positive\nexperiences", 
            "Life\nsatisfaction"
          )
        )
      )
  )

@@

```{r time-correlation-anxiety}
# Function to wrangle draws at multiple levels and create scatterplots + ellipses
draw_scatterplot <- function(fit, beta, r_region, r_country, sd_country, cor_country) {
  # Get average and region-specific slopes
  r_region_draws <- fit %>% 
    spread_draws(
      b_val_year, 
      b_internet_year,
      r_region__val[region, term],
      r_region__internet[region, term]
    ) %>% 
    filter(term == "year") %>% 
    ungroup() %>% 
    # Fix names by replacing dot with line break
    mutate(region = str_replace(region, "\\.", "\n"))

>>>>

```{r}
fits <- distinct(gbd, cause) %>% 
  mutate(
    fit1 = map(
      cause, 
      ~read_rds(str_glue("output/brm-1-{.x}.rds"))
    ),
    fit2 = map(
      cause, 
      ~read_rds(str_glue("output/brm-2-{.x}.rds"))
    )
  )
```

## Model comparison

Compare 1 and 2 to examine how much model fit / variance explained changes when the internet predictors are added.

@@

```{r}
tmp_coefs <- fits_1 %>% 
  mutate(
    out = map(
      fit, 
      ~hypothesis(
        .x, 
        # Rescale coefficient here to years on %
        # Note self harm doesnt work now
        c(str_glue("val_year = 0")),
        scope = "coef",
        group = "region"
      )$hypothesis
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  mutate(
    across(
      where(is.numeric), 
      ~round(., 3)
    )
  ) %>% 
  mutate(result = str_glue('**{Estimate}**<br>[{CI.Lower}, {CI.Upper}]')) %>% 
  select(cause, region = Group, result)
tmp_coefs
pseudo_gwp <-
  bind_rows(
    distinct(gbd, region, year, val = NA) %>% 
      crossing(
        cause = fct_inorder(
          c(
            "Negative\nexperiences", 
            "Positive\nexperiences", 
            "Life\nsatisfaction"
          )
        )
      )
  )

@@

```{r time-correlation-anxiety}
# Function to wrangle draws at multiple levels and create scatterplots + ellipses
draw_scatterplot <- function(
    fit, beta, r_region, r_country, sd_country, cor_country
) {
  # Get average and region-specific slopes
  r_region_draws <- fit %>% 
    spread_draws(
      b_val_year, 
      b_internet_year,
      r_region__val[region, term],
      r_region__internet[region, term]
    ) %>% 
    filter(term == "year") %>% 
    ungroup() %>% 
    # Fix names by replacing dot with line break
    mutate(region = str_replace(region, "\\.", "\n"))
